Structural Breaks in Inflation Dynamics within the European Monetary Union

### 2011-06-06 pkg/paper/Paper/draft.Rnw
small typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@112 b679b2f7-6539-45d0-a605-5ddcb976cde9

The results from the previous sections convey that the financial
crisis of 2008/9 did not have a significant effect on the inflation dynamics
in most of the European countries (except Ireland and Spain).
This may be somewhat surprising and is not enitrely correct. In fact,
there is a rather clear effect but as it is very short-lived and not
persistent it is not picked up by the structural break techniques.

>>>>

The results from the previous sections convey that the financial
crisis of 2008/2009 did not have a significant effect on the inflation dynamics
in most of the European countries (except Ireland and Spain).
This may be somewhat surprising and is not enitrely correct. In fact,
there is a rather clear effect but as it is very short-lived and not
persistent it is not picked up by the structural break techniques.
